---
title: "Curate dataset"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## About

### Description

The purpose of this script is to better organize the original data so that analyzing the dataset will be smoother and easier. In curating the dataset(s), we will be making changes to the original dataset, however these changes will be in the `data/derived/` folder instead.

### Usage

<!-- How to run this script: what input it requires and output produced -->

## Setup

```{r setup, include=FALSE}
# Script-specific options or packages
library(tidyverse) # data manipulation
library(readtext) # to read text into R
library(tidytext) # for tokenization/separating rows
```

## Run
```{r love_on_the_spectrum-idealized-dataset}
tribble(
  ~Series, ~Season, ~Episode,
  "Love on The Spectrum", "01", "01"
)
```
### Tidy the Data: Love on the Spectrum
```{r love_on_the_spectrum-read-files}
love_on_the_spectrum_files <-
  readtext(file = "../data/original/love_on_the_spectrum/*.srt",
           verbosity = 0) # suppresses warnings
```

```{r}
love_on_the_spectrum_files
```

```{r love_on_the_spectrum-metadata-clean-columns}
love_on_the_spectrum_files_separate <-
  love_on_the_spectrum_files %>%
  separate(col = doc_id, # column to break
           into = c("column_1", "column_2", "column_3", "column_4", "column_5"), # new columns created
           sep = "\\.",
           extra = "drop") # separator to break the doc_id column

love_on_the_spectrum_files_separate %>% # separated dataset
  select(-text) # do not show `text` column here
glimpse(love_on_the_spectrum_files_separate)
```

```{r love_on_the_spectrum-clean-columns-2}
love_on_the_spectrum_files_separate <-
  love_on_the_spectrum_files_separate %>%
  separate(col = column_5,
           into = c("Season", "Episode"),
           sep = "E")

love_on_the_spectrum_files_separate %>%
  select(-text)
```

```{r love_on_the_spectrum-unite-columns}
love_on_the_spectrum_files_unite <-
  love_on_the_spectrum_files_separate %>%
  unite(col = "Series", # new column name
        column_1:column_4, # columns to unite
        sep = " ") # separator to add between the column values
  
love_on_the_spectrum_files_unite %>% # united dataset
 select(-"text") # do not show the `text` column here
```

```{r love_on_the_spectrum_meta}
love_on_the_spectrum_meta <-
  love_on_the_spectrum_files_unite %>%
  mutate(Season = str_remove(Season,
                             pattern = "S")) # remove the 'S' from the value in Season

glimpse(love_on_the_spectrum_meta) # preview full dataset
```

### Curate Text: Love on the Spectrum
```{r}
love_on_the_spectrum_meta$text[1] %>% # subset the first observation of the text column
  str_trunc(width = 500) %>% # truncate the values to 500
  cat() # print the characters for inspection
```
```{r love_on_the_spectrum-clean-data}
love_on_the_spectrum_meta_lines <-
  love_on_the_spectrum_meta %>% # dataset with `text` column
  unnest_tokens(output = lines, # new column
                input = text, # input column
                token = "regex",
                pattern = "\\n", # split by new line anchor
                to_lower = FALSE) # do not lowercase the text

love_on_the_spectrum_meta_lines %>%# dataset
  slice_head(n = 10) # preview the first 10 observations
```

```{r love_on_the_spectrum-regular-expression}
love_on_the_spectrum_meta_lines %>%
  filter(str_detect(lines, "^\\d")) %>% # detect lines starting with a digit
  slice_sample(n = 10) # a random sample of 10 observations from the entire dataset
```
```{r love_on_the_spectrum-regular-expressions-to-remove}
love_on_the_spectrum_meta_lines_clean <-
  love_on_the_spectrum_meta_lines %>%
  filter(!str_detect(lines, "^\\d")) %>% # detect lines starting with a digit
  mutate(lines = str_remove(lines, "^-\\s")) %>% # remove leading '-' from each line
  filter(!str_detect(lines, "^\\[[a-z]")) %>% # remove lines starting with `[` before a lowercase letter
  mutate(lines = str_remove_all(lines, "\\[.+\\]")) %>% # remove cues inside of brackets (ex. [man])
  filter(!str_detect(lines,"^<.+?>.*")) %>% # remove lines starting with HTML tags
  mutate(lines = str_remove_all(lines, "<.+?>"))
# remove all HTML tags
```

```{r}
love_on_the_spectrum_curated <-
  love_on_the_spectrum_meta_lines_clean %>%
  group_by(Series, Season, Episode) %>% # grouping
  summarise(Dialogue = str_flatten(lines, collapse = " ")) %>% # collapse lines single observations for each series, season, episode combination
  ungroup() %>% # remove grouping attributes
  mutate(Dialogue = str_trim(Dialogue, side = "both")) # trim any leading or trailing whitespace from the united/flattened lines in dialogue
```
```{r}
love_on_the_spectrum_curated %>%
  mutate(Dialogue = str_trunc(Dialogue, 200)) 
```

### Tidy the Data: Love is Blind
```{r love_is_blind-read-files}
love_is_blind_files <-
  readtext(file = "../data/original/love_is_blind/*.srt",
           verbosity = 0) # suppresses warnings
glimpse(love_is_blind_files) # preview the structure of the dataset}

```

```{r love_is_blind-metadata-clean-columns}
love_is_blind_files_separate <-
  love_is_blind_files %>%
  separate(col = doc_id, # column to break
           into = c("column_1", "column_2", "column_3", "column_4", "Episode Title"), # new columns created
           sep = "\\.",
           extra = "drop") # separator to break the doc_id column

love_is_blind_files_separate %>% # separated dataset
  select(-text) # do not show `text` column here
glimpse(love_is_blind_files_separate)

```

```{r love_is_blind-clean-columns-2}
love_is_blind_files_separate <-
  love_is_blind_files_separate %>%
  separate(col = column_4,
           into = c("Season", "Episode"),
           sep = "E")

love_is_blind_files_separate %>%
  select(-text)
```

```{r love_is_blind-unite-columns}
love_is_blind_files_unite <-
  love_is_blind_files_separate %>%
  unite(col = "Series", # new column name
        column_1:column_3, # columns to unite
        sep = " ") # separator to add between the column values
  
love_is_blind_files_unite %>% # united dataset
 select(-"text") # do not show the `text` column here
```

```{r love_is_blind_meta}
love_is_blind_meta <-
  love_is_blind_files_unite %>%
  mutate(Season = str_remove(Season,
                             pattern = "S")) # remove the 'S' from the value in Season

glimpse(love_is_blind_meta) # preview full dataset}
```

### Tidy the Dataset: Love is Blind
```{r}
love_is_blind_meta$text[1] %>% # subset the first observation of the text column
  str_trunc(width = 500) %>% # truncate the values to 500
  cat() # print the characters for inspection
```

```{r love_is_blind-clean-data}
love_is_blind_meta_lines <-
  love_is_blind_meta %>% # dataset with `text` column
  unnest_tokens(output = lines, # new column
                input = text, # input column
                token = "regex",
                pattern = "\\n", # split by new line anchor
                to_lower = FALSE) # do not lowercase the text

love_is_blind_meta_lines %>%# dataset
  slice_head(n = 10) # preview the first 10 observations}

```

```{r love_is_blind-regular-expressions-to-remove}
love_is_blind_meta_lines_clean <-
  love_is_blind_meta_lines %>%
  filter(!str_detect(lines, "^\\d")) %>% # detect lines starting with a digit
  mutate(lines = str_remove(lines, "^-\\s")) %>% # remove leading '-' from each line
  filter(!str_detect(lines, "^\\[[a-z]")) %>% # remove lines starting with `[` before a lowercase letter
  mutate(lines = str_remove_all(lines, "\\[.+\\]")) %>% # remove cues inside of brackets (ex. [man])
  filter(!str_detect(lines,"^<.+?>.*")) %>% # remove lines starting with HTML tags
  mutate(lines = str_remove_all(lines, "<.+?>"))
# remove all HTML tags}
```

```{r}
love_is_blind_curated <-
  love_is_blind_meta_lines_clean %>%
  group_by(Series, Season, Episode,) %>% # grouping
  summarise(Dialogue = str_flatten(lines, collapse = " ")) %>% # collapse lines single observations for each series, season, episode combination
  ungroup() %>% # remove grouping attributes
  mutate(Dialogue = str_trim(Dialogue, side = "both")) # trim any leading or trailing whitespace from the united/flattened lines in dialogue
```

## Finalize
```{r love_on_the_spectrum-write-to-disk}
fs::dir_create(path = "../data/derived/love_on_the_spectrum/")
write_csv(love_on_the_spectrum_curated, # curated dataset
          file = "../data/derived/love_on_the_spectrum/love_on_the_spectrum_curated.csv")
```

```{r love_on_the_spectrum-create-dictionary}
data_dic_starter <- function(data, file_path) {
  # Function:
  # Creates a .csv file with the basic information
  # to document a curated dataset
  
  tibble(variable_name = names(data), # column with existing variable names
         name = " ", # column for human-readable names
         description = " ") %>%
    write_csv(file = file_path) # write to disk
} %>%

data_dic_starter(data = love_on_the_spectrum_curated, # curated dataset
                 file_path = "../data/derived/love_on_the_spectrum/love_on_the_spectrum_curated_dictionary.csv") 
```

```{r love_is_blind-write-to-disk}
fs::dir_create(path = "../data/derived/love_is_blind/")

write_csv(love_is_blind_curated, # curated dataset
          file = "../data/derived/love_is_blind/love_is_blind_curated.csv")
```

```{r love_is_blind-create-dictionary}
data_dic_starter <- function(data, file_path) {
  # Function:
  # Creates a .csv file with the basic information
  # to document a curated dataset
  
  tibble(variable_name = names(data), # column with existing variable names
         name = " ", # column for human-readable names
         description = " ") %>%
    write_csv(file = file_path) # write to disk
} %>%

data_dic_starter(data = love_is_blind_curated, # curated dataset
                 file_path = "../data/derived/love_is_blind/love_is_blind_curated_dictionary.csv")
```

### Log
The results of this script is our original dataset that we made edits to, which is now the derived dataset (since we didn't want to make edits to the original data). We get clean datasets (columns and rows that are better organized) for both Love on the Spectrum and Love is Blind so we are able to analyze the data easier.

<!-- Any description that will be helpful to understand the results of this script and how it contributes to the aims of the project -->

### Session

<details><summary>View session information</summary>

```{r, child="_session-info.Rmd"}
```

</details>

```{r cleanup, echo=FALSE}
rm(list = ls()) # clean working environment
```

## References
