---
title: "Do Language Differences Exist Between Adults on the Autism Spectrum and Adults Who Are 'Typically Developed'?"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## Project title

Language Differences Between Adults on the Autism Spectrum and Adults Who Are 'Typically Developed


### Research area and problem

After discussing what I wanted to do in class during our workshop, I have decided to sort of switch gears and focus on language differences among *adults* on the Autism Spectrum and those Typically Developing Adults, especially in the world of dating. The previous research I did found that there are language differences among children who are on the spectrum and those who are "typically developing," [@tek2014].

### Research aim and question

My aim is to look at the transcripts of Love on the Spectrum (sometimes referred to as LOTS in code chunks throughout), the Netflix series which follows individuals on the Autism spectrum as they navigate through love and romantic relationships, and Love is Blind, a show about dating with individuals who are not on the Spectrum and falling in love with someone they've never seen (sometimes referred to as LIB in code chunks throughout). For the purpose of this project, we are asking if there are differences in language among Autistic adults and Adults who are typically developed? If so, what are these differences and what domains are these differences in?

## Reproduce

View the READ.md file located in `data/original/open_subtitles/` in order to view how to acquire the data for this project.

### Session

<details>

<summary>

View session information

</summary>

```{r}
sessioninfo::session_info()
```

</details>

```{r cleanup, echo=FALSE}
rm(list = ls()) # clean working environment
```

## References
