---
title: "Do Language Differences Exist Between Adults on the Autism Spectrum and Adults Who Are 'Typically Developed'?"
date: "`r Sys.Date()`"
bibliography: references.bib
biblio-style: apalike
---

## Project title

A possible title for this project could be *Do Language Differences Exist Between Adults on the Autism Spectrum and Adults Who Are 'Typically Developed'?*

<!-- Add overview of the project here. -->

### Research area and problem

After discussing what I wanted to do in class during our workshop, I have decided to sort of switch gears and focus on language differences among *adults* on the Autism Spectrum and those Typically Developing Adults, especially in the world of dating. The previous research I did found that there are language differences among children who are on the spectrum and those who are "typically developing," [@tek2014].

### Research aim and question

My aim is to look at the transcripts of Dating on the Spectrum, the Netflix series, and find a similar type of show featuring those without a reported Developmental Disability. Are there differences in language development among Autistic adults and Adults who are typically developed? If so, what are these differences and what domains are these differences in?

## Reproduce

View the READ.md file located in `data/original/open_subtitles/` in order to view how to acquire the data for this project.

### Session

<details>

<summary>

View session information

</summary>

```{r}
sessioninfo::session_info()
```

</details>

```{r cleanup, echo=FALSE}
rm(list = ls()) # clean working environment
```

## References
